### 2023-03-06 csf2024/limitations.tex
update.

\section{Limitations and Future Work}
\label{sec:limitations}
Despite the effectiveness of~\systemname{}, it has the following limitations:

\noindent\textbf{Sandbox Dependency:} \systemname{} assumes the availability of a sandbox and consequently inherits all the limitations of the corresponding sandbox.~\eg Programs should be compilable with the sandbox compiler.
Also, as shown in~\sect{subsec:programoverhead}, the performance of the partitioned applications mainly depends on the sandbox.
However, our implementation is not dependent on one specific sandbox and can be easily extended to other sandboxes. As part of our future work, we will extend our implementation to other sandboxes.

>>>>

\section{Limitations and Future Work}
\label{sec:limitations}
Despite the effectiveness of~\systemname{}, it has limitations:

\noindent\textbf{Sandbox Dependency:} \systemname{} assumes the availability of a sandbox and consequently inherits all the limitations of the corresponding sandbox.~\eg Programs should be compilable with the sandbox compiler.
Also, as shown in~\sect{subsec:programoverhead}, the performance of the partitioned applications mainly depends on the sandbox.
However, our implementation is not dependent on one specific sandbox and can be easily extended to other sandboxes. As a future work, we will extend our implementation to other sandboxes.

### 2023-03-06 csf2024/oldintroduction.tex
update.

\emph{Checked C}~\cite{tarditi2018checked} as a
practical target to which to convert legacy/active C code. 
Checked C
extends C with \emph{checked pointer
  types} which are restricted by the compiler to spatially safe uses (temporal safety is underway~\cite{checkedc:temporal}).
Such pointers have one of three possible types, \ptrT{|$T$|}, \arrT{|$T$|},
or~\ntarrT{|$T$|} (\ptr, \arr, and \ntarr{} for short), representing a
pointer to a single element, array of elements, or null-terminated
array of elements of type $T$, respectively. The latter two have an
associated \emph{bounds annotation}; e.g., a declaration \arrT{int}
\code{p} : \code{count(n)} says that \code{p} is a pointer to an \code{int} array
whose size is \code{n}.
%
Checked C's Clang/LLVM-based compiler represents checked
pointers as system-level memory words, i.e., without
``fattening'' metadata, ensuring backward compatibility.
The compiler uses these bounds annotations to add dynamic checks prior to
checked pointer accesses, to prevent spatial safety violations.
These run-time checks can often be proved redundant and removed by LLVM, yielding good performance.
%, and leverages LLVM to optimize away run-time
%checks, yielding good performance.
%
Tarditi et al.~\cite{tarditi2018checked} reported average
run-time overheads of 8.6\% on a small benchmark suite, and
\cite{duanrefactoring} found essentially no overhead when running
Checked C-converted portions of the FreeBSD kernel.

@@

% How to highlighgt code in minted
% highlightlines={1-3}, highlightcolor=red

\begin{listing}[t!]
  \begin{tabular}{c c}
    \begin{minipage}[b]{.22\textwidth}
\inputminted[mathescape, escapeinside=||, fontsize=\tiny{}]{c}{examples/orig1.c}
    \end{minipage} &
    \begin{minipage}[b]{.22\textwidth}
\inputminted[mathescape, escapeinside=||, fontsize=\tiny{}]{c}{examples/orig2.c}
    \end{minipage} \\
   (a) Original C code & (b) After initial conversion.\\
  \end{tabular}
\caption{(Contrived) Example demonstrating various phases of.}
\label{lst:comb}
\end{listing}

>>>>

\emph{Checked C}~\cite{tarditi2018checked} as a
practical target to which to convert legacy/active C code. 
Checked C
extends C with \emph{checked pointer
  types} which are restricted by the compiler to spatially safe uses (temporal safety is underway~\cite{checkedc:temporal}).
Such pointers have one of three possible types, \ptrT{T}, \arrT{T},
or~\ntarrT{T} (\ptr, \arr, and \ntarr{} for short), representing a
pointer to a single element, array of elements, or null-terminated
array of elements of type $T$, respectively. The latter two have an
associated \emph{bounds annotation}; e.g., a declaration \arrT{int}
\code{p} : \code{count(n)} says that \code{p} is a pointer to an \code{int} array
whose size is \code{n}.
%
Checked C's Clang/LLVM-based compiler represents checked
pointers as system-level memory words, i.e., without
``fattening'' metadata, ensuring backward compatibility.
The compiler uses these bounds annotations to add dynamic checks prior to
checked pointer accesses, to prevent spatial safety violations.
These run-time checks can often be proved redundant and removed by LLVM, yielding good performance.
%, and leverages LLVM to optimize away run-time
%checks, yielding good performance.
%
Tarditi et al.~\cite{tarditi2018checked} reported average
run-time overheads of 8.6\% on a small benchmark suite, and
\cite{duanrefactoring} found essentially no overhead when running
Checked C-converted portions of the FreeBSD kernel.

@@

% How to highlighgt code in minted
% highlightlines={1-3}, highlightcolor=red
\ignore{
\begin{listing}[t!]
  \begin{tabular}{c c}
    \begin{minipage}[b]{.22\textwidth}
\inputminted[mathescape, escapeinside=||, fontsize=\tiny{}]{c}{examples/orig1.c}
    \end{minipage} &
    \begin{minipage}[b]{.22\textwidth}
\inputminted[mathescape, escapeinside=||, fontsize=\tiny{}]{c}{examples/orig2.c}
    \end{minipage} \\
   (a) Original C code & (b) After initial conversion.\\
  \end{tabular}
\caption{(Contrived) Example demonstrating various phases of.}
\label{lst:comb}
\end{listing}
